%% start of file `template.tex'.
%% Copyright 2006-2011 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref}
\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[orange]{classic}                  % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{marvosym}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths

\usepackage{enumitem}

\date{06/11/2014}

\firstname{Tom}
\familyname{Ruttle}
\phone{07816 499253}
\email{tom@tomruttle.com}
\homepage{http://www.tomruttle.com}

\begin{document}
\maketitle
Technologist with particular interests in APIs, micro-services and containers. Certified Scrum Master. Mostly working with Node.js.

\section{Experience}

\cventry{2012--}{Developer}{BMJ}{London}{}{Lead developer for BMJ Quality and BMJ Job Reviews API.
\begin{itemize}[label=\textbullet]
\item Designed and wrote the bulk of a Node.js Hypermedia API supporting an Angular.js front-end. Product was first-to-market due to our choices of technology and agile methodology.
\item Oversaw and managed the major refactoring of a large Drupal application: monolithic codebase was broken down into loosely-coupled modules.
\item Investigated, prototyped, advocated, documented, and implemented a variety of DevOps tools. Now exclusively using Docker clusters for development work, have built tools for other developers, and am involved in the development of Puppet modules for Docker orchestration.
\item "Voice of technology" on a steering committee. I have been assessing the requirements of customers (business team, end-users, and partners) and breaking them down into services.
\item Current project is an XML document transformation/validation suite built in a functional reactive style in Node.js. It utilises the Seneca.js micro-services framework and has 99\% Mocha test coverage.
\end{itemize}}

\cventry{2010--2012}{Drupal Product Consultant}{Firmstep}{Cambridge}{}{Delivering highly customised Drupal 7 websites to customers in the public sector as part of an agile team.
\begin{itemize}[label=\textbullet]
\item Devised and ran product training for groups of between two and twelve and all levels of IT experience.
\item Wrote documentation for both internal and customer use
\item Liaised between project management, customers, and developers
\end{itemize}}

\cventry{2005--2010}{Intern}{Firmstep}{Cambridge}{}{Built e-forms for customers in the public sector; acted as consultant to customers for company products; tested new releases of company products; some first-line support}{}

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{2006--2010}{\small{Master of Physics (MPHYS) in Physics with Philosophy}}{\newline{}University of York}{}{\small{Grade: \textit{2:1}}}{}
\cventry{2003--2005}{A-Levels in Computing, Maths, Economics, Physics}{\newline{}Hills Road Sixth Form College}{Cambridge}{Grades (respectively): \textit{A, B, B, B}}{}

\section{Extra-Curricular}

\cvline{Skydiving}{\small{Participated in 42-way formations in Summer 2014.\newline{}Have competed in 4-way Nationals competitions from 2010-2014.\newline{}Won silver medal in national 8-way skydiving championships, Rookie class, 2011.\newline{}University Colours awarded for service to University of York Skydiving Club. Positions held: Member (2006--2008); Social Secretary (2008--2009); Treasurer (2009--2010).}}

\end{document}
