\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{burgundy}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\date{11/08/2018}

\name{Tom}{Ruttle}
\email{tom@tomruttle.com}
\homepage{www.tomruttle.com}
\social[github]{tomruttle}

\begin{document}

\makecvtitle

Technologist with particular interests in APIs, micro-services and containers. Certified Scrum Master. Mostly working with Node.js.

\section{Technologies}

\begin{cvcolumns}
  \cvcolumn
    {Javascript}
    {
      \begin{itemize}
        \item ES2015+
        \item Node.js
        \item React
        \item Redux
        \item Flow
        \item Express
        \item Mocha
      \end{itemize}
    }

  \cvcolumn
    {Tooling}
    {
      \begin{itemize}
        \item Webpack
        \item Babel
        \item Eslint
      \end{itemize}
    }

  \cvcolumn
    {Infrastructure}
    {
      \begin{itemize}
        \item Docker
        \item Mongodb
        \item Jenkins
        \item Git
      \end{itemize}
    }

  \cvcolumn
    {Concepts}
    {
      \begin{itemize}
        \item Isomorphic JS
        \item Microservices
        \item Continuous Delivery
        \item XP
      \end{itemize}
    }
\end{cvcolumns}

\section{Experience}

\cventry
  {2017--}
  {Senior Software Engineer}
  {Tes}
  {Remote}
  {}
  {
    Stuff
  }

\cventry
  {2015--2017}
  {Software Engineer}
  {Tes}
  {London}
  {}
  {}

\cventry
  {2012--2015}
  {Developer}
  {BMJ}
  {London}
  {}
  {
    Lead developer for BMJ Quality and BMJ Job Reviews API.
    \begin{itemize}
      \item Designed and wrote the bulk of a Node.js Hypermedia API supporting an Angular.js front-end. Product was first-to-market due to our choices of technology and agile methodology.
      \item Oversaw and managed the major refactoring of a large Drupal application: monolithic codebase was broken down into loosely-coupled modules.
      \item Investigated, prototyped, advocated, documented, and implemented a variety of DevOps tools. Now exclusively using Docker clusters for development work, have built tools for other developers, and am involved in the development of Puppet modules for Docker orchestration.
      \item "Voice of technology" on a steering committee. I have been assessing the requirements of customers (business team, end-users, and partners) and breaking them down into services.
      \item Current project is an XML document transformation/validation suite built in a functional reactive style in Node.js. It utilises the Seneca.js micro-services framework and has 99\% Mocha test coverage.
    \end{itemize}
  }

\cventry
  {2010--2012}
  {Drupal Product Consultant}
  {Firmstep}
  {Cambridge}
  {}
  {
    Delivering highly customised Drupal 7 websites to customers in the public sector as part of an agile team.
    \begin{itemize}
      \item Devised and ran product training for groups of between two and twelve and all levels of IT experience.
      \item Wrote documentation for both internal and customer use
      \item Liaised between project management, customers, and developers
    \end{itemize}
  }

\cventry
  {2005--2010}
  {Intern}
  {Firmstep}
  {Cambridge}
  {}
  {
    Built e-forms for customers in the public sector; acted as consultant to customers for company products; tested new releases of company products; some first-line support
  }

\section{Education}

\cventry
  {2006--2010}
  {Master of Physics (\small{MPHYS}) in Physics with Philosophy}
  {\newline{}University of York}
  {}
  {2:1}
  {}

\cventry
  {2003--2005}
  {A-Levels in Computing, Maths, Economics, Physics}
  {\newline{}Hills Road Sixth Form College}
  {Cambridge}
  {A, B, B, B}
  {}

\section{Extra-Curricular}

\cvline
  {Travel}
  {
    Nomadic since January 2016
  }

\cvline
  {Skydiving}
  {
    Participated in 42-way formations in Summer 2014.
    \newline{}Have competed in 4-way Nationals competitions from 2010-2014.
    \newline{}Won silver medal in national 8-way skydiving championships, Rookie class, 2011.
    \newline{}University Colours awarded for service to University of York Skydiving Club. Positions held: Member (2006--2008); Social Secretary (2008--2009); Treasurer (2009--2010).
  }

\end{document}

% \subsection{Vocational}
% \cventry{year--year}{Job title}{Employer}{City}{}{General description no longer than 1--2 lines.\newline{}%
% Detailed achievements:%
% \begin{itemize}%
% \item Achievement 1;
% \item Achievement 2, with sub-achievements:
%   \begin{itemize}%
%   \item Sub-achievement (a);
%   \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
%     \begin{itemize}
%     \item Sub-sub-achievement i;
%     \item Sub-sub-achievement ii;
%     \item Sub-sub-achievement iii;
%     \end{itemize}
%   \item Sub-achievement (c);
%   \end{itemize}
% \item Achievement 3.
% \end{itemize}}
% \cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
% \subsection{Miscellaneous}
% \cventry{year--year}{Job title}{Employer}{City}{}{Description}
%
% \section{Master thesis}
%
% \cvitem{title}{\emph{Title}}
% \cvitem{supervisors}{Supervisors}
% \cvitem{description}{Short thesis abstract}
%
% \section{Languages}
%
% \cvitemwithcomment{Language 1}{Skill level}{Comment}
% \cvitemwithcomment{Language 2}{Skill level}{Comment}
% \cvitemwithcomment{Language 3}{Skill level}{Comment}
%
% \section{Computer skills}
%
% \cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}
%
% \section{Extra 1}
%
% \cvlistitem{Item 1}
% \cvlistitem{Item 2}
% \cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}
%
% \section{References}
%
% \begin{cvcolumns}
%   \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%   \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%   \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
% \end{cvcolumns}
